Self Regulation Ontology Retest Analyses

### 2018-05-16 code/SRO_Retest_Analyses.Rmd
frisem prep

demog_rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
                     icc = rep(NA, length(numeric_cols)),
                     pearson = rep(NA, length(numeric_cols)))

@@

for(i in 1:length(numeric_cols)){
  demog_rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i], t1_df = test_demog, t2_df = retest_demog) 
  demog_rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i], t1_df = test_demog, t2_df = retest_demog)
  demog_rel_df[numeric_cols[i], 'pearson'] <- get_pearson(numeric_cols[i], t1_df = test_demog, t2_df = retest_demog)
}

demog_rel_df = demog_rel_df %>%
  mutate(var = row.names(.)) %>%
  select(var, icc, spearman, pearson) %>%
  arrange(-icc)

@@

@@

>>>>

demog_rel_df <- data.frame(icc = rep(NA, length(numeric_cols)))

@@

for(i in 1:length(numeric_cols)){
  demog_rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i], t1_df = test_demog, t2_df = retest_demog)
}

demog_rel_df = demog_rel_df %>%
  mutate(var = row.names(.)) %>%
  select(var, icc) %>%
  arrange(-icc)

@@

```{r}
test_demog$HowOftenHazardousCannabis
retest_demog$HowOftenHazardousCannabis

test_demog$CaffieneOtherSourcesDayMG
retest_demog$CaffieneOtherSourcesDayMG

test_demog$SpouseParentsComplainDrugUse
retest_demog$SpouseParentsComplainDrugUse

test_demog$OtherDebtAmount
retest_demog$OtherDebtAmount
```

@@

```{r}
demog_rel_df %>%
  ggplot(aes(icc))+
  geom_density(fill = 'grey', alpha = 0.7, color = NA)+
  xlab("ICC")+
  ylab("Density")

ggsave('DemogRelDist.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 5, units = "in", dpi=300)
```
